Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-17 paper/main.tex
Restyle chapter headers
Added design of SHA3lib

@@

\subsection{SHA3lib}
SHA3lib is built to mimic the functionality of
hashlib\footnote{\url{http://docs.python.org/library/hashlib.html}}, the
default python library for MD5, \ac{SHA}-1 and the \ac{SHA}-2 family. 
% TODO, figure or listing of what this means

>>>>

% Restyle chapter headers
\usepackage{fix-cm}
\makeatletter
\renewcommand{\@makechapterhead}[1]{%
  \vspace*{50\p@}%
  {\parindent \z@ \raggedright \normalfont
    \vspace{15pt}%
    \ifnum \c@secnumdepth >\m@ne
        %\hfill\huge\scshape \@chapapp\space
        \hfill\fontsize{60}{90}\selectfont \thechapter % Chapter number
        \par\nobreak
        \vskip 20\p@
    \fi
    \interlinepenalty\@M
    \hfill \Huge \scshape #1\par % Chapter title
    \vspace{5pt}
    \hrule
    \nobreak
    \vskip 40\p@
  }}
\makeatother

@@

\subsection{SHA3lib}
SHA3lib is built to mimic the functionality of
hashlib\footnote{\url{http://docs.python.org/library/hashlib.html}}, the
default python library for MD5, \ac{SHA}-1 and the \ac{SHA}-2 family. This
means that we built class names for each candidate on the form
candidatename+256 and that the classes included the following functions:

\begin{itemize}
    \item Constructur with an optional data element that does the same as
    Update()
    \item Update() takes data that should be considered in hashing 
    \item digest() that produce a raw byte-digest from submitted data
    \item hexdigest() that produce a hex representation of the digest
    \item copy() that copies the internal state of the function and produces a
    copy of the object.
\end{itemize}

\subsubsection{Design}
Our original goal was to make SHA3lib include functionality to support all
output lengths, and not only 256-bit. This was based on our observation that
the official \ac{NIST} submission packages include ``all-in-one''
implementations that support this. Later we observed that this is not the case
for all implementations in \ac{SUPERCOP}. Together with the fact that
Tahoe-\ac{LAFS} uses 256-bit output we in the end only included support for
256-bit output in SHA3lib. The design we have used is shown in Figure
\ref{fig:python:inheritance}, and does follow the initial idea that SHA3lib
should support multiple output lengths.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.6\columnwidth]{python-inheritance.pdf}
    \caption{Design of SHA3lib using echo as an example}
    \label{fig:python:inheritance}
\end{figure}

Basically the class echo resides in Cython and in C and is responsible for
bringing the C functionality of the C implementation to Python. By compiling
echo it will be made available for use in Python.  The class echo256 is a
simple python class which inherits from echo. The only action this class
actually takes is to set the output size to 256-bit. If the underlying
C-functions would have supported multiple output sizes the same could have been
done to incorporate those.
